Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models

### 2023-10-17 paper_version/main.tex
final check by Ralf

\begin{remark}
  \label{rem:coll}
  For the sake of simplicity, we only consider ion-electron collision in this work, but
extension to more species is straightforward. Such collisions can be well modelled by
friction terms, for instance \citep[][Sec. 5.6.2]{chen2016}
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. ln$\Lambda$ is called the \emph{Coulomb
  logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
effects, e.g. ionization and recombination, are not considered. For full details about the
modeling of these physical processes, readers are referred to
\cite[][Sec. 3.2]{fuchs_2021}.
\end{remark}

@@

We arrive at non-dimensional equations by following the rescaling procedure of
\cite[][Sec. 2.2]{degond_2017}.  First, a reference value for each quantity is
prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
interest, by which the reference velocity $\overline{v}$ is defined as
$\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are
$\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number
density, $\overline{T}$ for plasma temperature. On top of that, the reference pressure is
set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
reference value for the specific total energy and enthalpy is set to
$\overline{u}^2$. Also taking into account the physical constants, i.e. the reference
permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the
elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
parameters:
\begin{align*} 
  \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
  \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
  M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
  \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
  \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
  \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
  g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

By abuse of notation, the rescaled variables share the same notation as before
rescaling. We neglect ionization and recombination but retain collision terms,
i.e. $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in
(\ref{equ:euler_}). The rescaled Euler-Maxwell system is
\begin{subequations}
\begin{align}
  \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
  \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
  \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
  \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
  \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix} +
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{pmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes
$e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and
$h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the
original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its
rescaled expression becomes
\begin{equation}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). \label{equ:rescaling_friction}
\end{equation}

@@

\begin{remark}
  \label{rem:limit}
  The limit \eqref{limit} represents a \emph{singular perturbation problem} in the sense
  that vanishing $\lambda$ changes the character of the PDE system. To be more specific,
  for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the
  quasi-neutral model, it responds instantaneously to other quantities according to the
  constraint (\ref{equ:maxwell_ampere_limit}). We replace
  (\ref{equ:maxwell_ampere_rescaled}) by the sum of the rotation of
  (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of
  (\ref{equ:maxwell_ampere_rescaled}). Meanwhile, due to the link between fluid momenta
  $n_*u_*$ and current in (\ref{equ:maxwell_euler_coupling}), the term
  $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to
  (\ref{equ:euler_rescaled}) and we end up with the following wave equation with the source
  terms:
  \begin{align}
    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= \mathbf{S}_1 + \mathbf{S}_2, \label{equ:E}
  \end{align}
  where
  \begin{align}
    \mathbf{S}_1 &= - \left(\sum_*\varepsilon_*^{-2}q_*^2n_*\right)\mathbf{E}, \\
    \mathbf{S}_2 &= \sum_* q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_*
    - \varepsilon_*^{-2}p_*\mathbb{I}\varepsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B}
    - q_*\varepsilon_*^{-2}\mathbf{R}^\text{coll}_*).
  \end{align}
  It is obvious in (\ref{equ:E}) that the electric fields propagate with finite speed
  (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ they
  respond instantaneously everywhere to local excitation (parabolic evolution/elliptic
  boundary value problems).
\end{remark}

@@

\begin{remark} For a geometric setting with non-trivial topology, e.g. with a tunnel,
  $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does guarantee the existence of a surface
  potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$. One needs to
  include co-homology vector fields \cite{Hiptmair_2021}.
\end{remark}

@@

No plasma fills the non-conducting domain $\Omega_N$ (see Fig.~\ref{fig:domain_sketch}),
and, consequently, the Maxwell system in $\Omega_N$ reduces to 
\begin{subequations}
  \label{eq:mxon}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}
In a non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$
is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are
redundant as long as they are satisfied at initial time. Nonetheless, as the system
approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for the
$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Schemes based on this set
of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence
constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold
numerically when $\lambda^2$ becomes extremely small.

@@

Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a (k+1)-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.~\ref{fig:orientation}.

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{c c l l}
    \hline
         Matrix & Size & Incidence relation & Intuition  \\
    \hline
         $\mathbb{D}\ (\Tilde{\mathbb{D}})$ & $N_V \times N_A\ (N_{\Tilde{V}} \times N_{\Tilde{A}})$ & cell $\rightarrow$ face & discrete divergence \\
         $\mathbb{C}\ (\Tilde{\mathbb{C}})$ & $N_A \times N_L\ (N_{\Tilde{A}} \times N_{\Tilde{L}})$ & face $\rightarrow$ edge & discrete rotation \\
         $\mathbb{G}\ (\Tilde{\mathbb{G}})$ & $N_L \times N_P\ (N_{\Tilde{L}} \times N_{\Tilde{P}})$ & edge $\rightarrow$ vertex & discrete gradient
         \\
    \hline
    \end{tabular}
    \caption{Summary of incidence matrices}
    \label{tab:incidence_mat}
\end{table}

@@

Note that the auxiliary edges might not be straight and the auxiliary faces might not be
flat as is shown in Fig.~\ref{fig:illustraion_dual_boundary}, which necessitates a
versatile data structure to include such situations. In the following, the auxiliary
entities would be treated as dual entities, which limits the validity of the relations in
Tab.~\ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$. For a more
systematic illustration that considers the boundary dual entities, see
\cite[][Sec. 5]{hip_1999}.

@@

A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.

@@

The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
primal mesh $\mathcal{M}$. As is mentioned in Section~\ref{sec:BC}, the zero-magnetic-flux
boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
$(\nabla\times\mathbf{E}) \cdot \mathbf{n} = 0$, which paves the way for a surface scalar
potential $\varphi:\partial\Omega\to\mathbb{R}$ such that the tangential component
$\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$. This remains
true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section~\ref{sec:BC})
are discretized in the following way:
\begin{center}
    \vspace{-0.5cm}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm,
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \centering
        \begin{subequations}
            \begin{align}
            d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
            e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \label{equ:bc_1}
            \end{align}
        \end{subequations}
    \end{minipage}
\end{center}
where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$
to all the primal verices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
represented by $\mathbb{GX}_\varphi$.

@@

We employ the finite volume method (FVM) to discretize the Euler system. The Euler
equations (\ref{equ:euler_}) can be cast into the form of conservation law with source
terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ stands for $m$
conservative variables;
$\mathbf{f}(\mathbf{U}) : \Omega \times [0,T] \rightarrow \mathbb{R}^{3 \times m}$ is the flux
function depending on $\mathbf{U}$; $\mathbf{RHS} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ is the source
term. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
$\mathbf{U} := [n, n\mathbf{u}, ne]$.

>>>>

\begin{remark}
  \label{rem:coll}
  For the sake of simplicity, we only consider ion-electron collision in this work, but
extension to more species is straightforward. Such collisions can be well modelled by
friction terms, for instance \citep[][Sec. 5.6.2]{chen2016}
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{\emph{ln}}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. \emph{ln}$\Lambda$ is called the \emph{Coulomb
  logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
effects, e.g. ionization and recombination, are not considered. For full details about the
modeling of these physical processes, readers are referred to
\cite[][Sec. 3.2]{fuchs_2021}.
\end{remark}

@@

We arrive at non-dimensional equations by following the rescaling procedure of
\cite[][Sec. 2.2]{degond_2017}.  First, a reference value for each quantity is
fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
interest, by which the reference velocity $\overline{v}$ is defined as
$\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are
$\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
denoted by $\overline{u}$ for the plasma drift velocity, $\overline{n}$ for the plasma number
density, $\overline{T}$ for the plasma temperature. On top of that, the reference pressure is
set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
reference value for the specific total energy and enthalpy is set to
$\overline{u}^2$. Also taking into account the physical constants, i.e. the reference
permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the
elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
parameters:
\begin{align*} 
  \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
  \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
  M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
  \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
  \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
  \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
  g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

Though rescaled, we keep the notations for the various quantities. We neglect ionization and recombination but retain collision terms,
i.e. $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in
(\ref{equ:euler_}). The rescaled Euler-Maxwell system is
\begin{subequations}
\begin{align}
  \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
  \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
  \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
  \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
  \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix} +
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{pmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes
$e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and
$h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the
original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its
rescaled expression becomes
\begin{equation}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). \label{equ:rescaling_friction}
\end{equation}

@@

\begin{remark}
  \label{rem:limit}
  The limit \eqref{limit} represents a \emph{singular perturbation problem} in the sense
  that vanishing $\lambda$ changes the character of the PDE system. To be more specific,
  for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the
  quasi-neutral model, it responds instantaneously to other quantities according to the
  constraint (\ref{equ:maxwell_ampere_limit}). We replace
  (\ref{equ:maxwell_ampere_rescaled}) by the sum of the rotation of
  (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of
  (\ref{equ:maxwell_ampere_rescaled}). Meanwhile, due to the link between fluid momenta
  $n_*u_*$ and current in (\ref{equ:maxwell_euler_coupling}), the term
  $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to
  (\ref{equ:euler_rescaled}) and we end up with the following wave equation with the source
  terms:
  \begin{align}
    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= \mathbf{S}_1 + \mathbf{S}_2, \label{equ:E}
  \end{align}
  where
  \begin{align}
    \mathbf{S}_1 &= - \left(\sum_*\varepsilon_*^{-2}q_*^2n_*\right)\mathbf{E}, \\
    \mathbf{S}_2 &= \sum_* q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_*
    - \varepsilon_*^{-2}p_*\mathbb{I}\varepsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B}
    - q_*\varepsilon_*^{-2}\mathbf{R}^\text{coll}_*).
  \end{align}
  It is obvious in (\ref{equ:E}) that the electric field propagates with finite speed
  (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ it
  responds instantaneously everywhere to local excitation (parabolic evolution/elliptic
  boundary value problems).
\end{remark}

@@

\begin{remark} For a geometric setting with non-trivial topology, e.g. with a tunnel,
  $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does not guarantee the existence of a surface
  potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$. One needs to
  include co-homology vector fields \cite{Hiptmair_2021}.
\end{remark}

@@

No plasma fills the non-conducting domain $\Omega_N$ (see Fig.~\ref{fig:domain_sketch}),
and, consequently, the Maxwell system in $\Omega_N$ reduces to 
\begin{subequations}
  \label{eq:mxon}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}
In a non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$
is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are
redundant as long as they are satisfied at initial time. Nonetheless, as the system
approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for the
$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) is no longer enforced. Schemes based on this set
of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence
constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold
numerically when $\lambda^2$ becomes extremely small.

@@

Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a $(k+1)$-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.~\ref{fig:orientation}.

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{c c l l}
    \hline
         Matrix & Size & Incidence relation & Operator  \\
    \hline
         $\mathbb{D}\ (\Tilde{\mathbb{D}})$ & $N_V \times N_A\ (N_{\Tilde{V}} \times N_{\Tilde{A}})$ & cell $\rightarrow$ face & discrete divergence \\
         $\mathbb{C}\ (\Tilde{\mathbb{C}})$ & $N_A \times N_L\ (N_{\Tilde{A}} \times N_{\Tilde{L}})$ & face $\rightarrow$ edge & discrete rotation \\
         $\mathbb{G}\ (\Tilde{\mathbb{G}})$ & $N_L \times N_P\ (N_{\Tilde{L}} \times N_{\Tilde{P}})$ & edge $\rightarrow$ vertex & discrete gradient
         \\
    \hline
    \end{tabular}
    \caption{Summary of incidence matrices}
    \label{tab:incidence_mat}
\end{table}

@@

Note that the auxiliary edges might not be straight and the auxiliary faces might not be
flat as is shown in Fig.~\ref{fig:illustraion_dual_boundary}, which necessitates a
versatile data structure to include such situations. In the following, the auxiliary
entities will be treated as dual entities, which limits the validity of the relations in
Tab.~\ref{tab:incidence_relation} to the interior part of $\Tilde{\mathcal{M}}$. For a more
systematic illustration that considers the boundary dual entities, see
\cite[][Sec. 5]{hip_1999}. A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.

@@

@@

The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
primal mesh $\mathcal{M}$. As is mentioned in Section~\ref{sec:BC}, the zero-magnetic-flux
boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
$(\nabla\times\mathbf{E}) \cdot \mathbf{n} = 0$, which paves the way for a surface scalar
potential $\varphi:\partial\Omega\to\mathbb{R}$ such that the tangential component
$\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$. This remains
true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section~\ref{sec:BC})
are discretized in the following way:
\begin{center}
    \vspace{-0.5cm}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm,
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \centering
        \begin{subequations}
            \begin{align}
            d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
            e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \label{equ:bc_1}
            \end{align}
        \end{subequations}
    \end{minipage}
\end{center}
where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$
to all the primal vertices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
represented by $\mathbb{GX}_\varphi$.

@@

We employ the finite volume method (FVM) to discretize the Euler system. The Euler
equations (\ref{equ:euler_}) can be cast into the form of a conservation law with source
terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ stands for $m$
conservative variables;
$\mathbf{f}(\mathbf{U}) : \Omega \times [0,T] \rightarrow \mathbb{R}^{3 \times m}$ is the flux
function depending on $\mathbf{U}$; $\mathbf{RHS} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ is the source
term. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
$\mathbf{U} := [n, n\mathbf{u}, ne]$.
